---
title: "Gini Coefficient"
author: "annika nazanin"
date: "`r Sys.Date()`"
format: html
---

## Metrics of equality / equity

Calculate inequality using the Lorenz curve and the accompanying gini coefficient.

-   Calculate the Lorenz curve for each scenario, and for the baseline scenario.
-   Plot the Lorenz curve for each scenario and baseline scenario.
-   Calculate the Gini coefficient For each scenario.

### Calculate Lorenz curve

Create a graph of the Lorenz curve that looks like
this(https://en.wikipedia.org/wiki/Lorenz_curve), EXCEPT:

-   X axis is the cumulative share of people from lowest to highest income, 0 to
    100%
-   We could rank order everyone, or divide everyone into like 100 income groups
    or something
-   Y axis is the cumulative share of INEXUS

This is a useful spreadsheet example for how to actually calculate Lorenz curve
and Gini coeff: https://en.wikipedia.org/wiki/Income_inequality_metrics

```{r}
#| echo: false

```

### Plot Lorenz curve

```{r}
#| echo: false

```

### Calculate Gini coefficient

```{r}

```
