---
title: "AustinDataAnalyses"
author: "Nazanin"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---
## Setup
```{r setup, include=FALSE}
#library(tidycensus)
#library(sf)
#library(purrr)
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
pacman::p_load(
  tidyverse, # for the tidyverse framework
  viridis,
  scales, 
  forcats,
  aws.s3, 
  furrr,
  tictoc,
  stringr,
  caTools,
  ggthemes,
  SciViews
  )
```

## Parallelize using: furrr (using multiple cores to speed up)
```{r}
n_cores <- availableCores() - 1
plan(multiprocess, # multicore, if supported, otherwise multisession
     workers = n_cores) # the maximum number of workers

#Check
tic()
mean100 <- map(1:1000000, mean)
toc()

tic()
mean100 <- future_map(1:1000000, mean)
toc()
```


## Import Data
```{r}
#AWS info - set environment variables
Sys.setenv("AWS_DEFAULT_REGION"="us-east-2")
awsDF <- get_bucket_df("beam-core-act", prefix = "GPRAcities/Austin-Q4FY2021") # getting bucket   
data <- list() # creating list 
data <- awsDF$Key[grep("*.csv.zip$|*.csv.gz$", awsDF$Key)] #specify austin data objects
for (i in data) 
  {x <- aws.s3::s3read_using(read_csv, object=i, bucket="beam-core-act")
   j <- substr(i,28,nchar(i)-8)
   assign(j, x)
   remove(x)
}
```


## Data Wrangling
```{r}
#Sort PassengertoPathTraversal dataset by personID
austin.passengerToPathTraversal <- austin.passengerToPathTraversal[order(austin.passengerToPathTraversal$personID),]

# Filter Plans = TRUE to help us merge the datasets
austinPlansTrue <- austin.plan %>% 
  filter(austin.plan$planSelected == TRUE)

#Replace -Infinity with seconds 86400 in plans
austinPlansTrue$activityEndTime[austinPlansTrue$activityEndTime == "-Infinity"] <- "86400"
austinPlansTrue$legDepartureTime[austinPlansTrue$legDepartureTime == "-Infinity"] <- NA
austinPlansTrue$legTravelTime[austinPlansTrue$legTravelTime == "-Infinity"] <- NA

```


```{r}
#Replace negative values with missing values in households
austin.household$incomeValue[austin.household$incomeValue < 0] <- NA
austin.person$earning[austin.person$earning < 0] <- NA

#Replace negative values with missing values of distance in plans
austinPlansTrue$legRouteDistance[austinPlansTrue$legRouteDistance < 0] <- NA
```


```{r}
#Convert column types to double 
austin.trips <- austin.trips %>%
  mutate(legDepartureTime = as.double(legDepartureTime),
         legTravelTime = as.double(legTravelTime),
        startBlockGroup = as.double(startBlockGroup),
        endBlockGroup = as.double(endBlockGroup))

austin.activities <- austin.activities %>%
  mutate(legDepartureTime = as.double(activityEndTime),
        startBlockGroup = as.double(activityBlockGroup))

austinPlansTrue <- austinPlansTrue %>%  
  mutate(activityEndTime = as.double(activityEndTime),
         legDepartureTime = as.double(legDepartureTime),
         legTravelTime = as.double(legTravelTime))
```

```{r}
#Drop the decimals in time floor(x) rounds to the nearest integer that’s smaller than x
austinPlansTrue$activityEndTime <- floor(austinPlansTrue$activityEndTime)
```

```{r}
#Convert seconds to minutes in plans and pathtraversals
austinPlansTrue$activityEndTime <- austinPlansTrue$activityEndTime / 60
austinPlansTrue$legDepartureTime <- austinPlansTrue$legDepartureTime / 60
austinPlansTrue$legTravelTime <- austinPlansTrue$legTravelTime / 60
austinPlansTrue$legRouteTravelTime <- austinPlansTrue$legRouteTravelTime / 60
austin.pathTraversals$arrivalTime <- austin.pathTraversals$arrivalTime / 60
austin.pathTraversals$departureTime <- austin.pathTraversals$departureTime / 60
austin.pathTraversals$duration <- austin.pathTraversals$duration / 60
```

```{r}
#rounding time columns to 2 decimals
austinPlansTrue$activityEndTime <- round(austinPlansTrue$activityEndTime, digits = 2) 
austinPlansTrue$legDepartureTime <- round(austinPlansTrue$legDepartureTime, digits = 2)
austinPlansTrue$legTravelTime <- round(austinPlansTrue$legTravelTime, digits = 2)
austinPlansTrue$legRouteTravelTime <- round(austinPlansTrue$legRouteTravelTime, digits = 2)
austin.pathTraversals$arrivalTime <- round(austin.pathTraversals$arrivalTime, digits = 2)
austin.pathTraversals$departureTime <- round(austin.pathTraversals$departureTime, digits = 2)
austin.pathTraversals$duration <-round(austin.pathTraversals$duration, digits = 2)
```

```{r}
#Joining pass and path
austinPassPath <- full_join(austin.passengerToPathTraversal, austin.pathTraversals, by = c("pathTraversalID" = "PathTraversalID"), copy = FALSE, suffix = c(".x", ".y"))
```


```{r}
#rename personID to personId in passPath
austinPassPath <- austinPassPath %>% 
  rename(personId = personID )
#names(austinPassPath)[names(austinPassPath) == 'personID'] <- 'personId'
```


```{r}
#Joining plans, pop and households
austinPlansPophhPer <- full_join(austinPlansTrue, austin.populatio, by = c("personId"), copy = FALSE, suffix = c(".x", ".y"))
austinPlansPophhPer <- full_join(austinPlansPophhPer, austin.household, by = c("householdId"), copy = FALSE, suffix = c(".x", ".y"))
austinPlansPophhPer <- left_join(austinPlansPophhPer, austin.person, by = c("personId"="person_id"), copy = FALSE, suffix = c(".x", ".y"))
```


```{r}
#add columns year and scenarios
austinPlansPophhPer$year <- "2010"
austinPlansPophhPer$scenario <- "austin"
```

## Saving the dataset as a csv file
```{r}
#write.csv(x=austinPlansPophhPer, file="/home/shared/Data/CleanData/austin.PlanPop.Merged.csv", row.names = F)
```


## Including Plots
```{r}
#divide incomeValue to two levels
#austinPlansPophhPer$incomeLevel <- ifelse((austinPlansPophhPer$incomeValue < 14.706), "Low","High")

#divide incomeValue to five levels
austinPlansPophhPer <- austinPlansPophhPer %>%  
  mutate(incomeLevel = ntile(incomeValue,5))

austinPlansPophhPer <- austinPlansPophhPer %>%
  mutate(incomeLevel = as.character(incomeLevel))
```


```{r}
#Categorize age to 8 groups 
austinPlansPophhPer <- austinPlansPophhPer %>% 
  mutate(ageGroup = case_when(age.x < 16 ~ "Below 16",
                               age.x >= 16 & age.x < 18 ~ "16 - 18",
                               age.x >= 18 & age.x < 30 ~ "18 - 30",
                               age.x >= 30 & age.x < 40 ~ "30 - 40",
                               age.x >= 40 & age.x < 50 ~ "40 - 50",
                               age.x >= 50 & age.x < 60 ~ "50 - 60",
                               age.x >= 60 & age.x < 75 ~ "60 - 75",
                               age.x >= 75 ~ "75 and Above"))
```


```{r}
#label education
austinPlansPophhPer <- austinPlansPophhPer %>% 
  mutate(eduLabel = case_when(edu == 1 ~ "No schooling completed", 
                              edu == 2 ~ "Nursery school, preschool",
                              edu == 3 ~ "Kindergartern",
                              edu == 4 ~ "Grade 1",
                              edu == 5 ~ "Grade 2",
                              edu == 6 ~ "Grade 3", 
                              edu == 7 ~ "Grade 4",
                              edu == 8 ~ "Grade 5",
                              edu == 9 ~ "Grade 6",
                              edu == 10 ~ "Grade 7",
                              edu == 11 ~ "Grade 8",
                              edu == 12 ~ "Grade 9",
                              edu == 13 ~ "Grade 10",
                              edu == 14 ~ "Grade 11",
                              edu == 15 ~ "12th grade - no diploma",
                              edu == 16 ~ "Regular high school diploma",
                              edu == 17 ~ "GED or alternative credential",
                              edu == 18 ~ "Some college, but less than 1 year",
                              edu == 19 ~ " 1 or more years of college credit, no degree",
                              edu == 20 ~ "Associate's degree",
                              edu == 21 ~ "Bachelor's degree",
                              edu == 22 ~ "Master's degree",
                              edu == 23 ~ "Professional degree beyond a bachelor's degree",
                              edu == 24 ~ "Doctorate degree"))
```


```{r}
#Categorize legMode to 5 groups
austinPlansPophhPer <- austinPlansPophhPer %>% 
  mutate(legModeCat = case_when(legMode == "car_hov2" | legMode ==   "car_hov3" | legMode == "car" | legMode == "hov2_teleportation" | legMode == "hov3_teleportation" ~ "car",
                                legMode == "ride_hail" | legMode ==   "ride_hail_pooled" ~ "ride_hail",
                                 legMode == "walk" ~ "walk",
                                 legMode == "bike" ~ "bike",
                                 legMode == "bike_transit" | legMode ==   "walk_transit" | legMode == "drive_transit" ~ "transit"))
```


```{r}
# Compute the frequency of incomeLevel - the sum is equal to the number of rows
austinPlansPophhPer %>%
    group_by(incomeLevel) %>%
    summarise(counts = n())
```


```{r - data.table}
#library(data.table)
#austinFirstLeg1 <- data.table(austinPlansPophhPer)[, firstStopOfTheDay:= #activityType [ planElementIndex == 2], by=personId]
#detach("package:data.table", unload=TRUE)
```

## New variables "firstStopOfTheDay"
```{r - tidyverse}
austinFirstLeg <- austinPlansPophhPer %>% 
  group_by(personId) %>%
  mutate(firstStopOfTheDay=activityType[planElementIndex == 2])
```

```{r}
austinFirstLegAc <- austinFirstLeg %>%
  group_by(personId) %>%
  mutate(fromActivityType=lag(activityType))

austinFirstLegAct <- austinFirstLegAc %>%
  group_by(personId) %>%
  mutate(ToActivityType=lead(activityType))
```


## Select only the first trip 
```{r}
#Selecting the first legs only
austinFirstLegWork <- austinFirstLegAct  %>% 
    filter(planElementType == "beam.utils.scenario.PlanElement$Leg$@488c76c1" & planElementIndex == 1 & firstStopOfTheDay == "work")

```

## Removing NA 
```{r}
#Remove missing values from the columns we would like to plot
austinlegPlot <- austinFirstLegWork  %>%  filter(!is.na(incomeValue) & !is.na(age.x) & !is.na(legRouteDistance)& !is.na(legMode)& !is.na(race_id)& !is.na(edu)& !is.na(isFemale)& !is.na(earning))

#legTravelTime below 1000 min
austinlegPlotTT <- austinlegPlot  %>% 
    filter(legTravelTime < 1000)

#income below 200
austinlegPlotTTI <- austinlegPlotTT  %>% 
    filter(incomeValue < 200)

# Compute the frequency of legMode
modeCount <- austinlegPlot %>%
  group_by(legModeCat) %>%
  summarise(counts = round(n()/n_distinct(austinlegPlot$personId),3)) %>% 
  arrange(desc(counts))

# Preparing the file for plotting Mode-Gender
modeFCount <- austinlegPlot %>% 
  group_by(isFemale, legModeCat) %>%
  summarise(counts = if(isFemale == TRUE) (n()/42315) else (n()/52570))

   
   
austinFirstLeg <- austinPlansPophhPer %>% 
  group_by(personId) %>%
  mutate(firstStopOfTheDay=activityType[planElementIndex == 2])
```

```{r}
austinlegPlot %>%
    group_by(isFemale) %>%
    summarise(counts = n())
```

## Color Schemes (viridis)
```{r}
show_col(viridis_pal(option = "turbo")(30))
show_col(viridis_pal(option = "viridis")(30)
show_col(economist_pal()(6))
show_col(calc_pal()(12))
show_col(gdocs_pal()(20))
```

```{r}
options(ggplot2.continuous.colour="viridis")

#For discrete scales
scale_colour_discrete <- function(...) {
  scale_colour_brewer(..., palette="viridis")
}
```


## Mode - Frequency
```{r, echo=FALSE, fig.height=7, fig.width=7}
# Create the bar plot
ggplot(modeCount, aes(x = reorder(legModeCat, -counts), y = counts)) +
    geom_bar(fill = "#21918c", stat = "identity") +
    geom_text(aes(label = scales::percent(counts)), vjust = -0.3) +
    scale_y_continuous(labels = scales::label_percent(accuracy = 1L))+  
    xlab("Trip Mode")+ 
    ylab("Frequency")+
    theme_bw()
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## Histogram of Travel Time Frequency (ggplot)
```{r, echo=FALSE, fig.height=7, fig.width=7}
ggplot(austinPlansPophhPer, aes(x=legTravelTime)) +
  geom_histogram(fill="#5ec962", color="black")+
  #geom_vline(aes(xintercept=mean(legTravelTime)), color="blue", linetype="dashed")+
  labs(title="Histogram for Travel Time",x="Travel Time (Minutes)", y = "Frequency")+
  xlim(c(0,700))+
  ylim(c(0,500000))+
  scale_y_continuous(labels = scales::comma)+  
  theme_bw()
```

## Histogram of Distance Frequency
```{r, echo=FALSE, fig.height=7, fig.width=7}
ggplot(austinPlansPophhPer, aes(x=legRouteDistance)) +
  geom_histogram(fill="#5ec962", color="black")+
  #geom_vline(aes(xintercept=mean(legTravelTime)), color="blue", linetype="dashed")+
  labs(title="Histogram for Travel Distance",x="Distance (Meters)", y = "Frequency")+
  xlim(c(0,160000))+
  ylim(c(0,250000))+
  scale_y_continuous(labels = scales::comma)+  
  theme_bw()
```

## TravelTime - Earning - Gender 
```{r - scatter plot}
ggplot(data = austinlegPlot, aes(x = ln(earning), y = ln(legTravelTime)))+
    geom_point(aes(color = isFemale), size=1, stat = 'identity')+ 
    xlab("Earning (dollars)") + 
    ylab("Travel Time (minutes)")+
    scale_x_continuous(labels=scales::dollar_format())+
    #scale_color_viridis(discrete = TRUE, option = "H", begin = 0.4)+
    scale_colour_economist()+
    theme_bw()
```

## TravelTime - Income - Mode
```{r - scatter plot}
ggplot(data = austinlegPlotTTI, aes(x = ln(incomeValue), y = legTravelTime))+
    geom_point(aes(color = legModeCat), size=1, stat = 'identity')+ 
    xlab("Household Income (dollars)") + 
    ylab("Travel Time (minutes)")+
    scale_x_continuous(labels=scales::dollar_format())+
    scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    #scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```


## Mode - Distance
```{r - box plot}
austinlegPlot %>%
    ggplot(aes(x = reorder(legModeCat,-legRouteDistance), y = legRouteDistance)) +
    geom_boxplot()+
    #stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..), width = .75, linetype = "dashed")+ #adding mean line
    xlab("Mode") + 
    ylab("Travel Distance")+
    theme_bw()
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## Mode - Income
```{r - box plot}
austinlegPlot %>%
    ggplot(aes(x = reorder(legModeCat,-incomeValue), y = incomeValue)) +
    geom_boxplot()+
    xlab("Mode") + 
    ylab("Income (dollars)")+
    scale_y_continuous(labels=scales::dollar_format())+
    theme_bw()
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

# Violin plot
```{r - violin plot}
austinlegPlot %>%
    ggplot(aes(x = reorder(legModeCat, -incomeValue), y = incomeValue)) +
    geom_violin()+
    stat_summary(fun = "mean", geom = "point", color = "black")+
    xlab("Mode") + 
    ylab("Household Income (dollars")+
    scale_y_continuous(labels=scales::dollar_format())+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

# Mode - Income Level 
```{r - bar plot}
austinlegPlot %>%
    ggplot(aes(x = legModeCat)) +
    geom_bar(aes(fill = incomeLevel), position = "dodge")+
    scale_fill_viridis(discrete = TRUE, option = "D")+
    scale_y_continuous(name="Frequency", labels = scales::comma)+
    xlab("Travel Mode") + 
    theme_bw()
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```


## TravelTime - Race
```{r - box plot}
austinlegPlotB250 %>%
    ggplot(aes(x = reorder(race_id,-legTravelTime), y = legTravelTime)) +
    geom_boxplot()+
    xlab("Race") + 
    ylab("Travel Time (minutes)")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## Mode - Gender
```{r - bar plot}
ggplot(modeFCount, aes(x = reorder(legModeCat, -counts), y = counts, fill = isFemale)) +
    geom_bar(position = "dodge", stat = "identity")+
    geom_text(aes(label = scales::percent(counts)), position = position_dodge(width = .9),    # move to center of bars
vjust = -0.5,    # nudge above top of bar 
size = 3) +
    scale_fill_viridis(discrete = TRUE, option = "H", begin = 0.2)+
    scale_y_continuous(labels = scales::label_percent(accuracy = 1L))+  
    xlab("Trip Mode")+ 
    ylab("Frequency")+
    theme_bw()
```


## TravelTime-CarOwnership

```{r}
austinlegPlotB250 %>%
    ggplot(aes(x = reorder(cars,-legTravelTime), y = legTravelTime)) +
    geom_boxplot()+
    xlab("Car Ownership") + 
    ylab("Travel Time (minutes)")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

## TravelTime - Age

```{r - box plot}
austinlegPlotB250 %>%
    ggplot(aes(x = reorder(ageGroup,-legTravelTime), y = legTravelTime)) +
    geom_boxplot()+
    xlab("Age (years)") + 
    ylab("Travel Time (minutes)")+
    theme_bw()
```

## TravelTime - Education

```{r - bar plot}
austinlegPlot %>%
    ggplot(aes(x = eduLabel)) +
    geom_bar()+
    scale_fill_viridis(discrete = TRUE, option = "H", begin = 0.7)+
    scale_y_continuous(name="Frequency", labels = scales::comma)+
    xlab("Education")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```


```{r - box plot}
austinlegPlotB250 %>%
    ggplot(aes(x = reorder(eduLabel,-legTravelTime), y = legTravelTime)) +
    geom_boxplot()+
    xlab("Education Level") + 
    ylab("Travel Time (minutes)")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

```

## TravelTime - Distance
```{r - scatter plot}
ggplot(data = austinlegPlot, aes(x = legRouteDistance, y = legTravelTime))+
    geom_point(size=1, stat = 'identity')+ 
    xlab("Distance (meters)") + 
    ylab("Travel Time (minutes)")+
    #scale_color_viridis(discrete = TRUE, option = "H", begin = 0.4)+
    scale_colour_economist()+
    theme_bw()
```

## TravelTime - DepartureTime
```{r - scatter plot}
ggplot(data = austinlegPlot, aes(x = legDepartureTime, y = legTravelTime))+
    geom_point(size=1, stat = 'identity')+ 
    xlab("Departure Time (meters)") + 
    ylab("Travel Time (minutes)")+
    #scale_color_viridis(discrete = TRUE, option = "H", begin = 0.4)+
    scale_colour_economist()+
    theme_bw()
```

