---
title: "SFActivitySimOutput"
author: "Nazanin"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
ifelse(packageVersion("dplyr") > 1, "The installed version of dplyr package is greater than or equal to 1.0.0", update.packages("dplyr"))
```


```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse, # for the tidyverse framework
  viridis,
  scales, 
  forcats,
  aws.s3, 
  furrr,
  tictoc,
  stringr,
  caTools,
  ggthemes,
  SciViews,
  yaml,
  purrr,
  janitor
  )
```


## Parallelize using: furrr (using multiple cores to speed up)
```{r}
n_cores <- availableCores() - 1
plan(multisession, # multicore, if supported, otherwise multisession
     workers = n_cores) # the maximum number of workers
```


## Import Data
```{r}
#AWS info - set environment variables
Sys.setenv("AWS_DEFAULT_REGION"="us-east-2")
awsDF <- get_bucket_df("beam-outputs", prefix = "pilates-outputs/austin-2010-2018-central/2018") # getting bucket   
data <- list() # creating list 
data <- awsDF$Key[grep("^final.*.csv$", awsDF$Key)] #specify data objects  
for (i in data) 
  {x <- aws.s3::s3read_using(read_csv, object=i, bucket="beam-outputs")
   j <- substr(i,5,nchar(i)-3)
   assign(j, x)
   remove(x)
}
```

```{r}
Sys.setenv("AWS_DEFAULT_REGION"="us-east-2")
awsDF <- get_bucket_df("beam-core-act", prefix = "ActivitySimOutput/100Households-BayArea") # getting bucket 
data <- list() # creating list 
data <- awsDF$Key[grep("*.csv$", awsDF$Key)] #specify austin data objects
for (i in data) 
  {x <- aws.s3::s3read_using(read_csv, object=i, bucket="beam-core-act")
   j <- substr(i,41,nchar(i)-5)
   assign(j, x)
   remove(x)
}

```


```{r eval=FALSE, include=FALSE}
#read .yaml file
#tripModeChoice <- aws.s3::s3read_using(read_yaml, object = "ActivitySimOutput/100Households-BayArea/trip_mode_choice.yaml", bucket = 'beam-core-act')
```

## Events File
```{r eval=FALSE, include=FALSE}
#AWS info - set environment variables
Sys.setenv("AWS_DEFAULT_REGION"="us-east-2")
awsDF <- get_bucket_df("beam-outputs", prefix = "pilates-outputs/austin-2010-2018-central/2018") # getting bucket   
data <- list() # creating list 
data <- awsDF$Key[grep("*final_*.csv$", awsDF$Key)] #specify austin data objects
for (i in data) 
  {x <- aws.s3::s3read_using(read_csv, object=i, bucket="beam-outputs")
   j <- substr(i,50,nchar(i)-2)
   assign(j, x)
   remove(x)
}
```

```{r}
Sys.setenv("AWS_DEFAULT_REGION"="us-east-2")
data = aws.s3::s3read_using(read_csv, object ="pilates-outputs/austin-2010-2018-central/2018/final_trip_mode_choice_raw.csv", bucket = 'beam-outputs')

```

```{r}
#Joining households and persons
households <- households[order(households$household_id),]
persons <- persons[order(persons$household_id),]

ActSimPerhh <- left_join(persons, households, by = c("household_id"), copy = FALSE, suffix = c(".x", ".y"))
```

```{r}
#Joining tours, households and persons
tour <- tour[order(tour$person_id, tour$tour_id),]
ActSimTourPerhh <- left_join(tour, ActSimPerhh, by = c("person_id"), copy = FALSE, suffix = c(".x", ".y"))
```

```{r eval=FALSE, include=FALSE}
#Export the file
#write.csv(x=ActSimTourPerhh, file="/Shared-Work/Data/CleanData/ActSimInexusPlots.csv", row.names = F)
```

```{r}
#Joining trips, tours, households and persons
trip <- trip[order(trip$person_id, trip$tour_id),]
ActSimTourTrip <- left_join(trip, ActSimTourPerhh, by = c("person_id","tour_id"), copy = FALSE, suffix = c(".x", ".y"))
```

```{r}
#Joining trips, tours, households, persons and final_trip_mode
final_trip_mode_choice_value <- final_trip_mode_choice_value[order(final_trip_mode_choice_value$trip_id),]
ActSimModeChoice <- left_join(ActSimTourTrip, final_trip_mode_choice_value, by = c("trip_id"), copy = FALSE, suffix = c(".x", ".y"))
```

```{r}
#write.csv(x=ActSimModeChoice, file="/home/shared/Data/CleanData/ActSim.Merged.csv", row.names = F)
```

#Read sample data
```{r}
ActSimMerged_sample <- read_csv(file='C:/Shared-Work/Data/CleanData/ActSim.Merged_Sample.csv', show_col_types = FALSE) 

specT_sample <- read_csv(file='C:/Shared-Work/Data/CleanData/Spec.Transpose_sample.csv', show_col_types = FALSE)

specs_sample <- read_csv(file='C:/Shared-Work/Data/specs_sample.csv', show_col_types = FALSE) 

```

```{r}
ActSimSpecSample <- 
  group_by("trip_mode") %>% 
  mapply("*", ActSimMerged_sample[intersect(names(ActSimMerged_sample), names(specT_sample))],
       specT_sample[intersect(names(ActSimMerged_sample), names(specT_sample))])
```



#Transpose spec file (We should rename the index column to trip_mode or convert the index to the first column)
```{r eval=FALSE, include=FALSE}
rName <- spec_new$Expression
specT <- as.data.frame(t(spec[,-1])) 
colnames(specT) <- rName
#check the type of columns
#lapply(specT,class)
```

```{r}
#Save spec Transpose file
write.csv(x=specT, file="C:/Shared-Work/Data/CleanData/Spec.Transpose.csv")
```


```{r}
ActSimMerged <- read_csv(file='C:/Shared-Work/Data/CleanData/ActSim.Merged.csv', show_col_types = FALSE) 

specT <- read_csv(file='C:/Shared-Work/Data/CleanData/Spec.Transpose.csv', show_col_types = FALSE)

#ActSimSpec <- read_csv(file='C:/Shared-Work/Data/CleanData/ActSimSpec.csv', show_col_types = FALSE)
```

# Reneme the columns in specT
```{r}
colnames(specT)[37] <- "@c_ivt*odt_skims['HOV2TOLL_TIME']...37"
colnames(specT)[294] <- "@c_ivt*odt_skims['HOV2TOLL_TIME']...294"
```

```{r}
spec_new <- read_csv(file='C:/Shared-Work/Data/specs.csv', show_col_types = FALSE)
```

# Clean column names
```{r eval=FALSE, include=FALSE}
names(ActSimMerged) = make.names(names(ActSimMerged))
```


# Multiply ActSimMerged by specs file rowwise - mutatae(across(all))
```{r}
ActSimSpec <- ActSimMerged %>% 
  rowwise() %>% 
  mutate(across(all_of(spec_new$Expression), ~ . * spec_new[match(cur_column(), spec_new$Expression), match(trip_mode, names(spec_new))])) 
```

```{r}
#Save file
write.csv(x=ActSimMerged, file="C:/Shared-Work/Data/CleanData/ActSimSpec.csv", row.names = F)
```

#Calculate the utility
```{r}
#ActSimMerged %>% mutate(utilities = rowSums(!is.na(select(., `sov_available == False`:`@adjust_tnc_shared`))))

#ActSimMerged$utilities <- apply(ActSimMerged[177:555], 1, function(x) sum(!is.na(x)))

#ActSimMerged %>% rowwise() %>% mutate(utilities=sum(!is.na(across(,`sov_available == False`:`@adjust_tnc_shared`))))


#ActSimMerged$utilities <- rowSums(ActSimMerged[grep("^var\\d+", names(ActSim_spec))], na.rm = TRUE)

ActSimSpec$mode_choice_utilities <- rowSums(ActSimSpec[,177:555], na.rm=TRUE)
```

#Calculate time
```{r}
ActSimSpec mutate(time = if primary_purpose == atwork %>% 
  @c_ivt*odt_skims/-0.0279
```

```{r}
#Save ActSim_spec  file
write.csv(x=ActSim_spec, file="C:/Shared-Work/Data/CleanData/ActSim_spec.csv", row.names = F)
```




#Tibbles don't have rownames - We convert Expressions to row names 
```{r}
#spec2 <- spec[,-1]
  
spec_new <- column_to_rownames(spec_new, var = "Expression")

#rownames(spec2) <- spec[[-1,]]
```


# Reneme the rows in spec (We don't have rownames in tibble to renames tham!)
```{r}
rownames(spec)[26] <- "@c_ivt*odt_skims['HOV2TOLL_TIME']...37"
rownames(spec)[293] <- "@c_ivt*odt_skims['HOV2TOLL_TIME']...294"
```

#Get the index of a column
```{r}
which(rownames(spec_new) == "@c_ivt * odt_skims['HOV2TOLL_TIME']...37")
```

```{r}
#Remove missing values from the columns we would like to multiply
cols <- intersect(colnames(ActSimMerged), colnames(specT[-1]))
#ActSimMergedRm <- ActSimMerged %>% drop_na(cols)
```


#Using across - cur_column "NOTWORKING"
```{r}
temp1 <- ActSimMerged %>%
  filter(trip_mode == 'SHARED2PAY') %>%
  mutate(across(c(), ~ . * t(spec[cur_group_rows('sov_available == False':'hov3_available == False')])))

```

#Check for SHARED2PAY only
```{r}
temp1 <- ActSimMerged %>%
  filter(trip_mode == 'SHARED2PAY') %>%
  select("trip_id","sov_available == False":"@adjust_tnc_shared") #%>% mutate(across(where(is.numeric), ~ . * spec[cur_column(), 'SHARED2PAY']))
```

```{r}
temp2 <- sweep(temp1,2, specT$SHARED2PAY[match(names(temp1),rownames(spec_new))],`*`)
```

```{r}
temp3 <- sweep(ActSimMerged[177:555],1, spec_new$TNC_SHARED[match(names(ActSimMerged[177:555]),rownames(spec_new))],`*`)
```


```{r}
a <- subset(ActSimMerged, select=177:555)
b <- subset(ActSimMerged_sample, select=177:180)
```

# Check missing values in the datasets
```{r}
missing_spec <- sapply(temp2, function(x) sum(is.na(x)))
```

```{r}
#missing_actMerged <- sapply(ActSimMerged, function(x) sum(is.na(x)))

missing_actMerged <- sapply(temp2, function(x) sum(is.na(x)));  missing_actMerged[missing_actMerged>0]
```

#Multiply all
```{r}
ActSim_spec <- sweep(b[],1, specs_sample[match(names(b),rownames(specs_sample))],`*`)
```

temp2 <- sweep(temp1[],2, spec_new$SHARED2PAY[match(names(temp1),rownames(spec_new))],`*`)


# Not Working
```{r}
ActSim_select <- ActSimMerged %>%
  #group_by("trip_mode") %>% 
  select("trip_mode", "sov_available == False":"@adjust_tnc_shared") #%>% 
  #keep(is.numeric) * specT %>% keep(is.numeric)
```

```{r}
ActSim_spec <- left_join(
  pivot_longer(ActSim_select, -trip_mode),
  pivot_longer(specT, -trip_mode),
  by = "name", suffix = c("2", "1")
) %>%
  mutate(value = value1 * value2) %>%
  select(trip_mode = trip_mode1, name, value) %>%
  pivot_wider()
```


#Change formats to matrix
```{r}
ActSim_mat <- as.matrix(ActSim_select[-1])
row.names(spec_mat) <- unlist(ActSim_select[1, ])

spec_mat <- as.matrix(spec_new[-1])
row.names(spec_mat) <- unlist(spec_new[, 1])
```

```{r}
lapply(colnames(ActSim_mat), function(x) ActSim_mat[rownames(spec_mat), x] * spec_mat)
```


```{r}
ActSimMerged %>% 
     #remove the 'Genes' column 
     select("trip_mode", "sov_available == False":"@adjust_tnc_shared") %>%
     #loop the other columns cbind with the Genes column
     map(~bind_cols(ActSimMerged['trip_mode'], Sample=.)) %>% 
     #left join with 'fixed_score' dataset by 'Genes'
     map(~left_join(specT, ., by = "trip_mode")) %>%
     #multiply the columns selected in 'vars' with 'Sample'
     map(~mutate_at(., vars(sov_available == False:@adjust_tnc_shared), funs(.*Sample))) %>%
     #remove the 'Sample' column from the list of tibbles
     map(~select(., -matches("Sample")))
```






















```{r}
#Joining ActSimModeChoice with specT
ActSimModeSpec <- left_join(ActSimModeChoice, specT, by = c("trip_mode"), copy = FALSE, suffix = c(".x", ".y"))
```


```{r}
cols <- intersect(colnames(ActSimMerged), colnames(specT[-1]))
ActSimMerged[cols] <- sweep(ActSimMerged[cols], 2, unlist(specT[cols]), `*`)
```








```{r}
library(purrr)
map2_dfc(select(ActSimModeChoice, 'sov_available == False' : '@adjust_tnc_shared'), select(specT, , 'sov_available == False' : '@adjust_tnc_shared'),  `*`) %>%
  bind_cols(select(ActSimModeChoice, -one_of(nm1)), .)
```






```{r}
#convert index to a column in specT
specT <- cbind(trip_mode = rownames(specT), specT)
rownames(specT) <- 1:nrow(specT)
```

```{r}
spec[-1][spec[-1]<0] <- 0
SpecT[-1][SpecT[-1]<0] <- 0
```




```{r}
clean_names(spec)
clean_names(ActSimMerged)
```


```{r}
data.frame(mapply('*', ActSimMerged[,c('sov_available == False':'@adjust_tnc_shared')],spec["WALK"]))
```

```{r}
temp1*spec[col(temp1)]
```


```{r}
temp1 <- ActSimMerged %>% 
  filter(trip_mode == 'WALK') %>% 
  select('trip_id','sov_available == False':'@adjust_tnc_shared')

temp2 <- SpecT %>% 
  filter(trip_mode == 'WALK') 

#multi <- temp1[,-1]*temp2[,-1]
```


```{r}
#mult <- data.frame(Map(function(x,y) if(all(is.numeric(x),is.numeric(y))) x * y
                          #else x, temp1, temp2))
```

#Dataset3[]<- mapply(`*`, ActSimMerged["sov_available == False": "@adjust_tnc_shared"], SpecT)


