---
title: "2021_12_5_Nazanin_ActSim_INEXUS_Plots"
author: "Nazanin"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
ifelse(packageVersion("dplyr") > 1, "The installed version of dplyr package is greater than or equal to 1.0.0", update.packages("dplyr"))
```


```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse, # for the tidyverse framework
  viridis,
  scales, 
  forcats,
  aws.s3, 
  furrr,
  tictoc,
  stringr,
  caTools,
  ggthemes,
  SciViews,
  yaml,
  janitor
  )
```


## Parallelize using: furrr (using multiple cores to speed up)
```{r}
n_cores <- availableCores() - 1
plan(multisession, # multicore, if supported, otherwise multisession
     workers = n_cores) # the maximum number of workers
```


## Import Data
```{r}
#AWS info - set environment variables
Sys.setenv("AWS_DEFAULT_REGION"="us-east-2")
awsDF <- get_bucket_df("beam-core-act", prefix = "deepDive/CleanData/SanFrancisco/Stacked") # getting bucket   
data <- list() # creating list 
data <- awsDF$Key[grep("*.csv$", awsDF$Key)] #specify austin data objects
for (i in data) 
  {x <- aws.s3::s3read_using(read_csv, object=i, bucket="beam-core-act")
   j <- substr(i,1,nchar(i)-2)
   assign(j, x)
   remove(x)
}

```


```{r}
#Joining households and persons
households <- households[order(households$household_id),]
persons <- persons[order(persons$household_id),]

ActSimPerhh <- left_join(persons, households, by = c("household_id"), copy = FALSE, suffix = c(".x", ".y"))
```

```{r}
#Joining tours, households and persons
tour <- tour[order(tour$person_id, tour$tour_id),]
ActSimTourPerhh <- left_join(tour, ActSimPerhh, by = c("person_id"), copy = FALSE, suffix = c(".x", ".y"))
```

```{r eval=FALSE, include=FALSE}
#Export the file
#write.csv(x=ActSimTourPerhh, file="/Shared-Work/Data/CleanData/ActSimInexusPlots.csv", row.names = F)
```

## INEXUS Plots


# ModeChoice Logsum - CarOwnership
```{r - boxplot}
ActSimTourPerhh %>%
    ggplot(aes(x = reorder(auto_ownership,-mode_choice_logsum), y = mode_choice_logsum)) +
    geom_boxplot()+
    xlab("Car Ownership") + 
    ylab("Mode Choice LogSum")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5))
```

# Destination Logsum - CarOwnership
```{r - boxplot}
ActSimTourPerhh %>%
    ggplot(aes(x = reorder(auto_ownership,-destination_logsum), y = destination_logsum)) +
    geom_boxplot()+
    xlab("Car Ownership") + 
    ylab("Destination LogSum")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5))
```


# ModeChoice Logsum - Income - Mode

```{r - scatterplot - income_in_thousands}
ggplot(data = ActSimTourPerhh, aes(x = income_in_thousands, y = mode_choice_logsum))+
    geom_point(aes(color = tour_mode), size=1, stat = 'identity')+ 
    xlab("Income (thousand dollars)") + 
    ylab("Mode Choice LogSum")+
    scale_x_continuous(labels=scales::dollar_format())+
    scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    #scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```


```{r - scatterplot - income - all 21 modes}
ggplot(data = ActSimTourPerhh, aes(x = income, y = mode_choice_logsum))+
    geom_point(aes(color = tour_mode), size=1, stat = 'identity')+ 
    xlab("Income (dollars)") + 
    ylab("Mode Choice LogSum")+
    scale_x_continuous(labels=scales::dollar_format())+
    scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    #scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```

```{r - all 21 modes}
ggplot(data = ActSimTourPerhh, aes(x = income, y = mode_choice_logsum))+
    geom_point(aes(color = tour_mode), size=1, stat = 'identity')+ 
    xlab("Income (dollars)") + 
    ylab("Mode Choice LogSum")+
    scale_x_continuous(labels=scales::dollar_format())+
    scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    #scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```

# Categorize tour_mode to 4 groups
```{r}
ActSimTourPerhh <- ActSimTourPerhh %>% 
  mutate(tourMode = case_when(tour_mode == "DRIVEALONEFREE" | tour_mode == "DRIVEALONEPAY" | tour_mode == "SHARED2FREE" | tour_mode ==   "SHARED2PAY" | tour_mode == "SHARED3FREE" | tour_mode == "SHARED3PAY"  ~ "CAR",
      tour_mode == "TNC_SHARED" | tour_mode ==   "TNC_SINGLE"| tour_mode == "TAXI" ~ "RIDE HAIL",
      tour_mode == "WALK" | tour_mode ==   "BIKE"  ~ "WALK/BIKE", 
      tour_mode == "WALK_COM" | tour_mode == "WALK_LRF" | tour_mode == "WALK_LOC" ~ "PUBLIC TRANSIT"))
```

```{r - 4 groups of modes}
ggplot(data = ActSimTourPerhh, aes(x = income, y = mode_choice_logsum))+
    geom_point(aes(color = tourMode), size=3, stat = 'identity')+ 
    xlab("Income (dollars)") + 
    ylab("Mode Choice LogSum")+
    scale_x_continuous(labels=scales::dollar_format())+
    scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```

# Urban-Rural
```{r}
ggplot(data = ActSimTourPerhh, aes(x = income, y = mode_choice_logsum, color = home_is_urban))+
    geom_point(size=3, stat = 'identity')+ 
    geom_smooth(method = "lm", se = FALSE)+
    xlab("Income (dollars)") + 
    ylab("INEXUS relative to average")+
    scale_x_continuous(labels=scales::dollar_format())+
    labs(title="Potential INEXUS", color='Residential Tract')+
  scale_color_manual(labels = c("non-urban", "urban"), values = c("green", "brown")) +
  #scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    #scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
    

```

#cut-off
```{r}
#income below 500k
ActSimTourPerhh <- ActSimTourPerhh  %>% 
    filter(income < 500000)
#logsum below 10
ActSimTourPerhh <- ActSimTourPerhh  %>% 
    filter(mode_choice_logsum < 10)
```

```{r}
ggplot(data = ActSimTourPerhh, aes(x = income, y = mode_choice_logsum))+
    geom_point(aes(color = tourMode), size=3, stat = 'identity')+ 
    xlab("Income (dollars)") + 
    ylab("Mode Choice LogSum")+
    scale_x_continuous(labels=scales::dollar_format())+
    #scale_color_viridis(discrete = TRUE)+
    #scale_color_gdocs()+ 
    scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```

```{r}
ggplot(data = ActSimTourPerhh, aes(x = income, y = mode_choice_logsum))+
    geom_point(aes(color = home_is_urban), size=3, stat = 'identity')+ 
    xlab("Income (dollars)") + 
    ylab("Mode Choice LogSum")+
    scale_x_continuous(labels=scales::dollar_format())+
    #scale_color_viridis(discrete = TRUE)+
    scale_color_gdocs()+ 
    #scale_color_calc()+
    #scale_colour_economist()+
    theme_bw()
```

# Histogram of logsum
```{r, echo=FALSE, fig.height=7, fig.width=7}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum)) +
  geom_histogram(fill="#5ec962", color="black")+
  #geom_vline(aes(xintercept=mean(legTravelTime)), color="blue", linetype="dashed")+
  labs(title="Histogram for Mode Choice LogSum", x="mode_choice_logsum", y = "Frequency")+
  xlim(c(0,700))+
  ylim(c(0,500000))+
  scale_y_continuous(labels = scales::comma)+  
  theme_bw()
```

# Mode Choice LogSum Frequency colored by Mode
```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = tourMode)) +
  geom_density(size=1)+
  #scale_color_viridis(discrete = TRUE, option = "viridis", begin = 0.2)+
  labs(x="Mode Choice LogSum", y = "Frequency")+
  #scale_colour_brewer(type = "div") +
  scale_color_gdocs()+ 
   theme_bw()
```

```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = income)) +
  geom_density() 
```

#divide income to 3 levels
```{r}
ActSimTourPerhh <- ActSimTourPerhh %>%
    mutate(incomeQuantile1 = ntile(income, 3))

ActSimTourPerhh$incomeQuantile[ActSimTourPerhh$incomeQuantile1 == "1"] <- "Low"

ActSimTourPerhh$incomeQuantile[ActSimTourPerhh$incomeQuantile1 == "2"] <- "Medium"

ActSimTourPerhh$incomeQuantile[ActSimTourPerhh$incomeQuantile1 == "3"] <- "High"
```

#Divide income in 2 groups
```{r}
median(ActSimTourPerhh$income, na.rm = TRUE)
ActSimTourPerhh$incomeLevel <- ifelse((ActSimTourPerhh$income < 106650), "Low","High")
```

# Mode Choice LogSum Frequency colored by Income Level
```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = incomeLevel)) +
  geom_density(size=1)+
  #scale_color_viridis(discrete = TRUE, option = "viridis", begin = 0.2)+
  labs(x="Mode Choice LogSum", y = "Frequency")+
  #scale_colour_brewer(type = "div") +
  scale_color_gdocs()+ 
   theme_bw()
```

# Mode Choice LogSum Frequency colored by Income Quantile
```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = incomeQuantile)) +
  geom_density(size=1)+
  #scale_color_viridis(discrete = TRUE, option = "viridis", begin = 0.2)+
  labs(title = "Potential INEXUS", x="INEXUS relative to average", y = "Frequency", color = "Household Income")+
  #scale_colour_brewer(type = "div") +
  #scale_color_discrete(breaks=c("High","Medium","Low"))+
  scale_color_gdocs(breaks=c("High","Medium","Low"))+ 
  theme_bw()
```


# Mode Choice LogSum Frequency colored by urban/rural
```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = home_is_urban)) +
  geom_density(size=1)+
  #scale_color_viridis(discrete = TRUE, option = "turbo", begin = 0.2)+
  labs(title = "Potential INEXUS", x="INEXUS relative to average", y = "Frequency", color='Residential Tract')+
  scale_color_manual(labels = c("non-urban", "urban"), values = c("green", "brown")) +
  #scale_colour_brewer(type = "div") +
  #scale_color_gdocs()+ 
   theme_bw()
```

#car ownership into two groups
```{r}
ActSimTourPerhh$car_ownership_status <- ifelse((ActSimTourPerhh$hh_cars == "none"), "no_car","at_least_one_car")
```


# Mode Choice LogSum Frequency colored by car/no car
```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = car_ownership_status)) +
  geom_density(size=1)+
  #scale_color_viridis(discrete = TRUE, option = "turbo", begin = 0.2)+
  labs(x="Mode Choice LogSum", y = "Frequency")+
  #scale_colour_brewer(type = "div") +
  scale_color_gdocs()+ 
  theme_bw()
```


# ModeChoice Logsum - CarOwnership
```{r - boxplot}
ActSimTourPerhh %>%
    ggplot(aes(x = reorder(car_ownership_status,-mode_choice_logsum), y = mode_choice_logsum)) +
    geom_boxplot()+
    xlab("Car Ownership") + 
    ylab("Mode Choice LogSum")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5))
```

# ModeChoice Logsum - CarOwnership
```{r - boxplot}
ActSimTourPerhh %>%
    ggplot(aes(x = reorder(hh_cars,-mode_choice_logsum), y = mode_choice_logsum)) +
    geom_boxplot()+
    xlab("Car Ownership") + 
    ylab("Mode Choice LogSum")+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5))
```


# Mode Choice LogSum Frequency colored by car/no car
```{r}
ggplot(ActSimTourPerhh, aes(x=mode_choice_logsum, color = hh_cars)) +
  geom_density(size=1)+
  ggtitle("Potential INEXUS") +
  theme(plot.title = element_text(hjust = 0.5))+
  #scale_color_viridis(discrete = TRUE, option = "turbo", begin = 0.2)+
  labs(x="INEXUS relative to average", y = "Frequency", color='Household Cars')+
  #scale_colour_brewer(type = "div") +
  scale_color_gdocs()+ 
  theme_bw()
```


```{r}
ActSimTourPerhh <- ActSimTourPerhh %>% 
  mutate(residentialTract = case_when(home_is_urban == "TRUE"  & home_is_rural == "FALSE" ~ "URBAN",
      home_is_rural == "TRUE" & home_is_urban == "FALSE"~ "RURAL",
      home_is_urban == "FALSE" & home_is_rural ==   "FALSE"   ~ "NEITHER"))
```

```{r}
#Export the file
#write.csv(x=ActSimTourPerhh, file="/Shared-Work/Data/CleanData/ActSimInexusFinal.csv", row.names = F)
```
